---
title: 'psychTestR and Google Sheets'
output: github_document
---

## 1. Install `googlesheets4`

Note that this is different from the `googlesheets` package which is obsolete.

```{r}
library(googlesheets4)
```

## 2. Create a Google authentication token.

Open your experiment's `app.R` in RStudio, and under the Session menu, set the working directory to the source file's directory. Then run the following code.

```{r, eval = FALSE}
sheets_auth(cache = '.')
```

You will be prompted to log into your Google account. Keep track of which e-mail you used to do it!

## 3. Make sure Git ignores the token.

You don't want to push that token to Git. Under the Git tab in RStudio, right click on the new file that will look something like `2325f32e235e64e8cc_my.name@gmail.com` and choose Ignore.

## 4. Copy following code chunk to your `app.R`.

Place it after your library imports.

```{r, eval = FALSE}
library(googlesheets4)

## Save function based on Harrison's elt_save_results_to_disk()
elt_save_results_to_google <- function(email, ssid) {
    code_block(
        function(state, opt, ...) {
            sheets_auth(cache = '.', email = email, use_oob = TRUE)
            results <-
                as.data.frame(
                    get_results(state, complete = TRUE, add_session_info = TRUE)
                ) %>%
                psychTestR:::list_cols_to_json()
            saved_data <- sheets_read(ssid, sheet = 1)
            if (nrow(saved_data) == 0) {
                sheets_write(results, ssid, sheet = 1)
            } else {
                sheets_append(results, ssid, sheet = 1)
            }
        }
    )
}
```

## 5. Replace your elt_save_results_to_disk() call.

Replace your call to `elt_save_results_to_disk(complete = TRUE)` with the following.

```{r, eval = FALSE}
elt_save_results_to_google(
    email = 'YOUR_EMAIL'
    ssid = 'YOUR_RESULTS_SHEET_ID'
)
```

What is your Sheet ID? In Google Sheets, if you copy and paste the web address of your spreadsheet, it will look something like this:

> https://docs.google.com/spreadsheets/d/5__2P-13920-efaj235efmvg/edit#gid=0

Everything between `d/` and `/edit` is the Sheet ID. Cut this part of the URL out, and put it in your `elt_save_results_to_google()` function.
