---
title: 'Using psychTestR for Music Cognition'
output: github_document
---

This week, we will learn how to create our own experiments with Peter Harrison's new `psychTestR` package. Please use this document as a companion to the extensive set of tutorials on his [package web site](https://pmcharrison.github.io/psychTestR/).

## Set up shinyapps.io

In order to run our experiments, we need to be able to host web sites with Shiny. You can do that inexpensively with shinyapps.io. Make an account, and then run these commands just once to set up your laptop.

```{r, eval = FALSE}
install.packages('rsconnect')
remotes::install_github('pmcharrison/psychTestR')
rsconnect::setAccountInfo(name='YOUR_NAME',
			  token='YOUR_TOKEN',
			  secret='YOUR_SECRET')
```


## Creating an experiment

In order to put our app online, we need to make a new directory in our repository with the app name (e.g., `everyday-test`). This directory needs to contain all of the code and supplemental information like CSV files. The code needs to go in a raw R script named `app.R` -- always! R scripts are like one gigantic code chunk, with no Markdown

```{r setup}
library(tidyverse)
library(psychTestR)
```

We start by loading the agreement prompts. The sliders in `psychTestR` don't allow us to label the scale points, and so it is better to use a multiple-choice question instead. We give each choice a name (`MSI1`, `MSI1`, etc.) in order to make it easier to write a scoring function later. The function inside `pmap` needs to handle every column in our CSV file.

```{r}
msi_agreement_prompts <- read_csv2('apps/w10-demo/gold-msi-agreement.csv')
msi_agreement <- 
    pmap(
        msi_agreement_prompts,
        function(id, prompt, is_positive) {
            NAFC_page(
                label = id,
                prompt = prompt,
                choices = 
                    c('MSI1', 'MSI2', 'MSI3', 'MSI4', 'MSI5', 'MSI6', 'MSI7'),
                labels = 
                    c(
                        'Completely disagree',
                        'Strongly disagree',
                        'Disagree',
                        'Neither agree nor disagree',
                        'Agree',
                        'Strongly agree',
                        'Completely agree'
                    )
            )
        }
    )
```

For the non-agreement questions, we want to use the same choice names for our scoring function, but we'll use the labels from the CSV file.

```{r}
msi_other_prompts <- read_csv2('apps/w10-demo/gold-msi-other.csv')
msi_other <-
    pmap(
        msi_other_prompts,
        function(id, prompt, score1, score2, score3, score4, score5, score6, score7, is_positive) {
            NAFC_page(
                label = id,
                prompt = prompt,
                choices = 
                    c('MSI1', 'MSI2', 'MSI3', 'MSI4', 'MSI5', 'MSI6', 'MSI7'),
                labels = 
                    c(score1, score2, score3, score4, score5, score6, score7)
            )
        }
    )
```

Finally, we join them all together with randomisation.

```{r}
msi_complete <- 
    join(
        one_button_page(
            'You will be given a series of statements about how you engage with music in your daily life. Please tell us how much you agree with them.'
        ),
        randomise_at_run_time(label = 'msi_agreement_order', logic = msi_agreement),
        one_button_page(
            'Now we have a few more questions about your formal music experience in the past.'
        ),
        randomise_at_run_time(label = 'msi_other_order', logic = msi_other),
        text_input_page(
            label = 'MSI39',
            prompt = 'The instrument I play best, including voice, is _____.'
        )
    )
```

Once we have a complete test, we set some options and make a test. You can look up the `shinythemes` package if you want to try other themes.

```{r}
my_options <-
    test_options(
        title = 'Everyday Listening 2020: Gold-MSI General',
        admin_password = 'delovely',
        researcher_email = 'j.a.burgoyne@uva.nl',
        theme = 'lumen'
    )
my_test <- make_test(
    elts = 
        join(
            one_button_page(
                'Welcome to my experiment! Let me give you some instructions.'
            ),
            get_basic_demographics(),
            msi_complete,
            elt_save_results_to_disk(complete = TRUE),
            final_page('Those are all of the questions we have. Thank you!')
        ),
    opt = my_options
)
```

Finally, let's run the app with Shiny!

```{r, eval = FALSE}
shiny::runApp(my_test)
```

When we are happy with the test, we need to end with a *bare* `make_test()` function, without storing it as a variable. For an example, look at the `apps` directory at the [course repository](https://github.com/jaburgoyne/everyday2020).

