---
title: 'Exploring the Spotify API'
output: github_document
---

### 1. Install the necessary packages.

- For this week, we need to have the `tidyverse` and `spotifyr` packages installed.

### 2. Create a `spotify.R` file to hide your login credentials (optional).

- Download the [sample `spotify.R`](./spotify.R) and save it to your project directory.
- Add `spotify.R` as a new line at the end of your `.gitignore` file,
which you can find in the Files pane.

### 3. Set up R.

- Use the RStudio Code menu to insert a new R chunk.
- Load the `tidyverse` and `spotifyr` libraries.
- Use the `source` command to load `spotify.R`.

```{r setup}
library(tidyverse)
library(spotifyr)
source('spotify.R')
```

### 3. Download and view features for your playlists.

- Collect the most listened tracks for each member in your group, from the [Spotify Wrapped](https://open.spotify.com/genre/2019-page) page.

```{r}
spotify_features <-
  ## Use the tribble() function to give one-word labels for your playlists, e.g.,
  ## type and subtype, or group member and year, plus the URIs for the Spotify
  ## user and playlist. Often the user is just 'spotify'.
  tribble(
    ~type, ~subtype, ~user, ~playlist,
    'Studying', 'Instrumental', 'spotify', '37i9dQZF1DX9sIqqvKsjG8',
    'Studying', 'Intense', 'spotify', '37i9dQZF1DX8NTLI2TtZa6',
    'Concentration', 'Electronic', 'spotify', '37i9dQZF1DX3XuTDjo5z5z',
    'Concentration', 'Natural', 'spotify', '37i9dQZF1DWYFCj3KyU0r0'
  ) %>% 
  ## This line downloads the features from Spotify.
  mutate(features = map2(user, playlist, get_playlist_audio_features)) %>% 
  ## Use the select() function to keep your label columns, plus the features.
  select(type, subtype, features) %>% 
  ## This line expands the features into a single table.
  unnest(features)
```

### 4. Explore statistical summaries.

- Use summarisation and grouping commands to explore the values of the Spotify features.
- `min()`
- `max()`
- `mean()`
- `median()`
- `sd()`
- `IQR()`
- Compare your results with the distribution of features in the Spotify documentation.
- Remember to think of differences in terms of standard deviations. As a rule of thumb, differences
- < 0.2 SD are considered too trivial to be of scientific interest,
- > 0.2 SD but < 0.5 SD are considered scientifically relevant but small,
- > 0.5 SD but < 0.8 SD are considered medium-sized, and
- > 0.8 SD are considered large, perhaps so large that there was no need to conduct an experiment.

```{r}
spotify_features %>% 
  ## Try different features and different summary functions.
  summarise(M = mean(danceability, SD = sd(danceability)))
```

```{r}
spotify_features %>% 
  ## Try grouping by group member and/or year.
  group_by(type, subtype) %>% 
  ## Try different features and different summary functions.
  summarise(M = mean(danceability, SD = sd(danceability)))
```

### 5. Explore with visualisations.

- We will learn more about visualisations later in the course, but here are some templates you can use to start with.
- See the [`ggplot` documentation](https://ggplot.tidyverse.org/) for more examples.

```{r}
spotify_features %>% 
  ggplot(aes(x = loudness)) +
  geom_histogram(binwidth = 5)
```

```{r}
spotify_features %>% 
  ggplot(aes(x = subtype, y = acousticness)) +
  geom_boxplot()
```


```{r}
spotify_features %>% 
  ggplot(aes(x = type, y = danceability, fill = subtype)) +
  geom_violin()
```

```{r}
spotify_features %>% 
  ggplot(aes(x = valence, y = energy)) + 
  facet_wrap(~ type) +
  stat_density_2d(
    geom = 'raster', 
    aes(fill = stat(density)), 
    contour = FALSE
  ) + 
  geom_jitter(colour = 'white', alpha = 0.5) + 
  coord_equal()
```

### 6. Push to Github.

- Use the Knit button in RStudio to preview how your page will look.
- Follow the directions in *Happy Git*, [Sections 16.4 to  16.7](https://happygitwithr.com/existing-github-first.html#stage-and-commit) to stage, commit, and push your changes to Github.
- After several minutes (and possibly several page refreshes), your changes should be visible from the github.io link you made earlier.

